Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-04-06 ms.tex
typose

This error budget is the same as that of \cite{planckdust} Equation 7. 
$c_{\nu_i}$ is the multiplicative calibration uncertainty for the intensity in 
each band. We have adopted the $c_{\nu_i}$ values listed in \cite{planckdust} 
Table 1. For the 217 GHz band, we have assigned $c_{217 GHz}$ = 0.54, from 
Table 11 of \cite{planckcalib}. $CMB$ represents the CMB intensity 
subtracted at the relevant pixel. $\delta0_{\nu_i}$ represents the uncertainty
in the offset used to tie \PLANCK~intensity to H\,\textsc{i}. We have adopted 
the  $\delta0_{\nu_i}$ values of \cite{planckdust} Table 1. $n_{\nu_i}$ 
represents the instrumental noise in the pixel of interest, and is taken to be 
the square root of the \verb|ii_cov| parameter that accompanies each 
\PLANCK~intensity map. In order to obtain reasonable fitting results at high 
latitude where the data is noisy, we include a prior on $T_2$:

>>>>

This error budget is the same as that of \cite{planckdust} Equation 7. 
$c_{\nu_i}$ is the multiplicative calibration uncertainty for the intensity in 
each band. We have adopted the $c_{\nu_i}$ values listed in \cite{planckdust} 
Table 1. For the 217 GHz band, we have assigned $c_{217 GHz}$ = 0.54, from 
Table 11 of \cite{planckcalib}. $CMB$ represents the CMB intensity 
subtracted at the relevant pixel. $\delta O_{\nu_i}$ represents the uncertainty
in the offset used to tie \PLANCK~intensity to H\,\textsc{i}. We have adopted 
the  $\delta O_{\nu_i}$ values of \cite{planckdust} Table 1. $n_{\nu_i}$ 
represents the instrumental noise in the pixel of interest, and is taken to be 
the square root of the \verb|ii_cov| parameter that accompanies each 
\PLANCK~intensity map. In order to obtain reasonable fitting results at high 
latitude where the data is noisy, we include a prior on $T_2$:
